---
title: "Introduction to StatComp20069"
author: "Yingying Xia"
date: "`2020-12-09`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp20069}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp20069__ is a simple R package developed to display two functions from my research project and all functions of my homework for the 'Statistical Computing' course. Two functions are considered, namely, _simple_conv2d_ (extract features with using filters(kernel)) and _MaxPool2d_ (reduce dimensionality and prevent overfitting). 


## _simple_conv2d_ and _MaxPool2d_

The source R code for _simple_conv2d_ is as follows:
```{r,eval=FALSE}
simple_conv2d <- function(img, kernel_size) {
  img_col = ncol(img)
  img_nrow = nrow(img)
  kernel_col = kernel_size[1]
  kernel_row = kernel_size[2]
  #generate norm 
  kernel <- matrix(data = rnorm(n = kernel_col * kernel_row, mean = 0, sd = 1), ncol = kernel_col)
  
  result <- matrix(nrow = (img_nrow - kernel_row + 1), ncol = (img_col - kernel_col + 1))
  
  for (i in c(1:(img_col - kernel_col+1))) {
    for (j in c(1:(img_nrow - kernel_row +1))) {
      result[j, i] <- sum(img[j:(j+kernel_row-1), i:(i+kernel_col-1)] * kernel)
    }
  }
  
  return(result)
}
```

And the source R code for _MaxPool2d_ is as follows:
```{r,eval=FALSE}
MaxPool2d <- function(hidden) {
  hidden_col = ncol(hidden)
  hidden_nrow = nrow(hidden)
  #generate norm 
  result <- matrix(nrow = ((hidden_nrow - 2)/2 + 1), ncol = ((hidden_col - 2)/2 + 1))
  
  for (i in c(1:((hidden_col - 2)/2 + 1))) {
    for (j in c(1:((hidden_nrow - 2)/2 + 1))) {
      result[j, i] <- max(hidden[j:((j+2)/2-1), i:(i+2-1)] )
    }
  }
  
  return(result)
}
```

In order to test _simple_conv2d_ and _MaxPool2d_,10*10 samples were randomly generated. The R code for benchmark _simple_conv2d_ and _MaxPool2d_ are as follows:

```{r warning=FALSE, eval=FALSE}
res1 <- simple_conv2d(img = matrix(data = rnorm(100), ncol = 10), kernel_size = c(5, 5))
res2 <- MaxPool2d(hidden = matrix(data = rnorm(100), ncol = 10))
res1
res2
dim(res1)
dim(res2)
```
As we can see,the first function changes the size of input layer into 6*6,it can be used to extract features and reduce dimensions of images in the application.And the second reduces the previous dimension by half,it is very effective in preventing overfitting.

